From rosmarqu@nmsu.edu Wed Jan 22 11:56:00 1997
Date: Wed, 22 Jan 1997 11:55:57 -0700 (MST)
X-Sender: rosmarqu@emmy.nmsu.edu
Mime-Version: 1.0
Content-Type: multipart/mixed; boundary="=====================_853959217==_"
To: smh@NMSU.Edu
From: rosmarqu@nmsu.edu (Rose Marquez)
Subject: 
X-Mailer: <PC Eudora Version 1.4>
X-Attachments: S:\ROSES\HOLIDAY\ABSTRCTS.TEX;S:\ROSES\HOLIDAY\ABSTRCTS.DVI;
Content-Length: 50201
X-Lines: 1005
Status: RO


--=====================_853959217==_
Content-Type: text/plain; charset="us-ascii"

Dear Susan:

I'm sending you both files, the .tex file and .dvi file, I'm not sure which 
one is the one you really need.


--=====================_853959217==_
Content-Type: text/plain; charset="us-ascii"

%% This document created by Scientific Word (R) Version 2.0


\documentclass[12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{sw20jart}

%TCIDATA{TCIstyle=Article/ART4.LAT,jart,sw20jart}

\setlength{\topmargin}{-.6in}
\setlength{\textheight}{9.0in}
\input tcilatex
\QQQ{Language}{
American English
}

\begin{document}


\begin{center}
{\Large {A B S T R A C T S } }

{\normalsize \smallskip\ }

{\normalsize %
******************************************************************* }
\end{center}

\vspace{.1in}

\noindent \textbf{Geir Agnarsson, }University of California at Berkeley

\noindent \textbf{On Functionals and Outside Corners of Monomial Ideals}

\smallskip\ 

\noindent Let $k$ be a field, $R$ a free $k$-algebra on some set, and $I$ a
two-sided ideal of $R$. We will present sufficient conditions on the ideal $%
I $ and the algebra $R$ for $I$ to have a finite basis of functionals $%
R\rightarrow k$. Thereby we get a generalization of F.S. Macaulay's result
from 1916, that every ideal $I$ of $k[X_1,\ldots ,X_n]$ has a finite basis
of functionals $k[X_1,\ldots ,X_n]\rightarrow k$. In this case we get
moreover that if $I$ has a Gr\"{o}bner basis consisting of $p$ elements,
then the number of functionals in such a basis is, for fixed $n$, bounded by
a $\Theta (p^{[n/2]})$-function. This function is closely related to the
maximal number of corners of a monomial ideal generated by $p$ monomials in $%
n$ variables.

\begin{center}
*******************************************************************
\end{center}

\vspace{.1in}\ 

\noindent \textbf{Mike Bardzell, }Salisbury State University

\noindent \textbf{A Lifted Gr\"{o}bner Basis for the Enveloping Algebra}

\smallskip\ 

\noindent In this talk we consider a finite-dimensional quotient of a path
algebra and demonstrate how its enveloping algebra can be modeled on a
computer for homological calculations. A method of lifting a reduced
Gr\"{o}bner basis from the original algebra to its enveloping algebra is
also presented.

\begin{center}
*******************************************************************
\end{center}

\vspace{.1in}\ 

\noindent \textbf{Lidia Filus, }Northeastern Illinois University

\noindent \textbf{Why Gr\"{o}bner Bases? Comparison of some methods for
solving systems of nonlinear equations}

\smallskip\ 

\noindent Comparisons with some of the fixed point algorithms will be
discussed. Questions regarding possibilities to apply Gr\"{o}bner Bases
ideas to these algorithms will be raised.

\smallskip\ 

\begin{center}
*******************************************************************
\end{center}

\vspace{.1in}\ 

\noindent \textbf{Tatiana Gateva-Ivanova, }American University in Bulgaria

\noindent \textbf{Noncommutative Gr\"{o}bner Bases in Skew-polynomial Rings}

\smallskip\ 

\noindent We study a class of graded standard finitely presented quadratic
algebras $A$ over a fixed field $K$, called binomial skew polynomial rings.
Following a classical tradition (and recent trend), we take a combinatorial
approach to study the algebraic properties of $A$. Our purpose is to exhibit
a class of non-commutative algebras with good algebraic properties among
which Noetherianness, being a domain, regularity, which can be read off a
presentation $A=K\left\langle X\right\rangle /(F)$, where $X=\left\{
x_1,...,x_n\right\} $ is a set of indeterminates of degree 1, $K\left\langle
X\right\rangle $ is the unitary free associative algebra generated by $X$
and $(F)$ is the two-sided ideal, generated by a finite set of homogeneous
polynomials.

Following $[2]$, a \textbf{binomial skew polynomial ring} is a graded
algebra $A=$ $K\left\langle X\right\rangle /(F)$, which has precisely $%
n(n-1)/2$ defining relations $F=\{x_jx_i-c_{ij}u_{ij}\left| \text{\\}\right.
1\leq i<j\leq n\},$ such that (a) $c_{ij}$ are non-zero coefficients; (b) $%
u_{ij}=x_{i^{\prime }}x_{j^{\prime }},$ for $1\leq i<j\leq n$, with $%
i^{\prime }<j$, $i^{\prime }<j^{\prime }$; (c) the set $F$ is a reduced
Gr\"{o}bner basis (w.r.t. the deg-lex ordering on the free semigroup $%
\left\langle X\right\rangle $) of the ideal $(F)$.

We give necessary and sufficient condition for Noetherianness of $A$ in case
that the set of relations $F$ is square-free. We show that the notion of
Gr\"{o}bner basis can be extended for modules over strictly ordered
algebras, so that an analogue of Bergman's Diamond Lemma holds (cf. [2],
2.2) and apply this for Noetherian skew polynomial rings with binomial
relations. The following result can be extracted from [2] and [3].

\smallskip\ 

\noindent \textbf{Theorem}\emph{\ Let }$A=K\left\langle X\right\rangle /(F)$%
, \emph{be a binomial skew-polynomial ring. Suppose the set of relations} $F$%
\emph{\ is square-free. Then the following conditions are equivalent:}

\begin{description}
\item[ ]  \emph{(1)} \emph{each} $x_ix_j,$\emph{\ with} $1\leq i<j\leq n$, 
\emph{appears in the right hand side of some relation in} $F$;

\item[ ]  \emph{(2)} $A$ \emph{is left Noetherian;}

\item[ ]  \emph{(3)} $A$ \emph{is right Noetherian;}

\item[ ]  \emph{(4) Any left ideal of }$A$\emph{\ has a finite Gr\"{o}bner
basis (with respect to some grading of} $A$\emph{;)}

\item[ ]  \emph{(5) Any right ideal of }$A$ \emph{has a finite Gr\"{o}bner
basis (with respect to some grading of }$A$; \emph{Furthermore, any of the
conditions (1) - (5) implies that}

\item[ ]  \emph{(a) the membership problem for finitely generated one-sided
ideals in }$A$ \emph{is decidable; }

\item[ ]  \emph{(b) }$A$ \emph{is a domain;}

\item[ ]  \emph{(c)} $A$ \emph{is regular in the sense of Artin-Schelter
(cf.[2]).}

\item[ ]  \emph{(d) the operator on} $X^2$ \emph{naturally defined by the
quadratic relations }$F$ \emph{satisfies the setheoretic Yang Baxter
equations.}
\end{description}

\begin{thebibliography}{1}
\bibitem[1]{1}  M. Artin, W. Schelter, Graded algebras of global dimension
3, \emph{Advances of Math.} \textbf{66} (1987), 171-216.

\bibitem[2]{2}  T. Gateva-Ivanova, Skew polynomial rings, \emph{J. Algebra, }%
\textbf{185} (1996), 710-753.

\bibitem[3]{3}  T. Gateva-Ivanova, M. Van den Bergh, Semigroups of I-type 
\emph{Preprint.}
\end{thebibliography}

\begin{center}
*******************************************************************
\end{center}

\vspace{.1in}\ 

\noindent \textbf{Susan Hermiller,} New Mexico State University

\noindent \textbf{Rewriting systems and 3-manifolds}

\smallskip\ 

\noindent The fundamental groups of most (conjecturally, all) closed
3-manifolds with uniform geometries have finite complete rewriting systems.
The fundamental groups of a large class of amalgams of circle bundles also
have finite complete rewriting systems. The general case remains open. This
is joint work with Mike Shapiro.

\begin{center}
*******************************************************************
\end{center}

\noindent \textbf{Anne Heyworth, }University of Wales

\noindent \textbf{Computerised left Knuth-Bendix procedure for enumerating
cosets }

\smallskip\ 

\noindent Using the presentation \TEXTsymbol{<}X,R\TEXTsymbol{>} of a group
G, and the generators of a subgroup H in G, and a monomial ordering on F(X)
one can do a left Knuth-Bendix completion. This gives a ``left-complete''
system that can be applied to the words in the free group F(X) to enumerate
the right cosets of H in G. I have computerised the process (using Axiom).
It is a valid alternative to the Todd-Coxeter process.

\begin{center}
*******************************************************************
\end{center}

\vspace{.1in}\ 

\noindent \textbf{Xenia Kramer,} New Mexico State University

\noindent \textbf{The Noetherian Property in Some Quadratic Algebras }

\smallskip\ 

\noindent We introduce a new class of noncommutative rings called \emph{%
pseudopolynomial rings}\/ and give sufficient conditions for such a ring to
be Noetherian. Pseudopolynomial rings are standard finitely presented
algebras over a field with some additional restrictions on their defining
relations---namely that the polynomials in a Gr\"{o}bner basis for the ideal
of relations must be homogeneous of degree 2---and on the Ufnarovskii graph $%
\Gamma (A)$. The class of pseudopolynomial rings properly includes the
generalized skew polynomial rings introduced by M.~Artin and W.~Schelter. We
use the graph $\Gamma (A)$ to define a weaker notion of almost commutative,
which we call \emph{almost commutative on cycles.} We show as our main
result that a pseudopolynomial ring which is almost commutative on cycles is
Noetherian. A counterexample shows that a Noetherian pseudopolynomial ring
need not be almost commutative on cycles.

\vspace{.1in}\ 

\noindent \textbf{Xenia Kramer,} New Mexico State University

\noindent \textbf{Combinatorial Homotopy of Simplicial Complexes}

\smallskip\ 

\noindent Combinatorial homotopy is an analog of the usual homotopy theory
of algebraic topology which is intended to reflect combinatorial features of
a simplicial complex. The combinatorial version of a path is a finite
sequence of simplices $\sigma _1,\sigma _2,\ldots ,\sigma _n$ in a complex $%
\Delta $ where for $1\leq i<n$, the dimension of $\sigma _i\cap \sigma
_{i+1} $ is at least $q$, for some previously set value $q$. Two paths are
homotopic in this combinatorial sense if one can be deformed to the other
while keeping the dimension of the intersection of adjacent simplices at
least $q$.

\smallskip\ 

\noindent The motivation for the study of combinatorial homotopy comes from
the analysis of complex information systems. The flow of traffic in such a
system is constrained by the underlying structure of the system; that is,
the dynamic behavior of a system is influenced by its static structure.
Combinatorial homotopy was introduced to describe features of that static
structure.

\smallskip\ 

\noindent In this talk, we will focus on the mathematics of combinatorial
homotopy. After defining it, we give an algorithm for computing it which
uses Gr\"{o}bner bases in a free associate algebra. This work was done in
collaboration with Reinhard Laubenbacher.

\begin{center}
\textbf{*}******************************************************************
\end{center}

\vspace{.1in}\ 

\noindent \textbf{Peter Malcolmson, }Wayne State University

\noindent \textbf{Gr\"{o}bner-Shirshov bases for quantum enveloping algebras}

\smallskip\ 

\noindent We give a method for finding Gr\"{o}bner-Shirshov bases for the
quantum enveloping algebras of Drinfel'd and Jimbo, show how the methods can
be applied to Kac-Moody algebras, and explicitly find the bases for quantum
enveloping algebras of type A (for the quantizing coefficient not an eighth
root of unity).

\begin{center}
*******************************************************************
\end{center}

\newpage\ 

\noindent \textbf{Eduardo do Nascimento Marcos, }IME-USP (Dept. de
Matematica) Brazil

\noindent \textbf{Graded Rings of Local Finite Representation Type}

\smallskip\ 

\noindent Graded Artin algebras whose category of graded modules is locally
of finite representation type are introduced. The representation theory of
such algebras is studied. In the hereditary case and in the stably
equivalent to hereditary case, such algebras are classified.

\begin{center}
*******************************************************************
\end{center}

\smallskip\ 

\noindent \textbf{Mike Newman,} Australian National University

\noindent \textbf{Some use of Knuth-Bendix in the study of groups}

\smallskip\ 

\noindent I will describe the use of Knuth-Bendix and other software for
proving that certain Engel groups are nilpotent.

\begin{center}
\ *******************************************************************
\end{center}

\vspace{.1in}

\noindent \textbf{Gretchen Ostheimer, }Tufts University

\noindent \textbf{Finding Matrix Representations for Polycyclic Groups}

\smallskip\ 

\noindent It has been known since the 1960's that a solvable group $G$ can
be embedded in $GL\left( n,Z\right) $ for some $n$ if and only if $G$ is
polycyclic. In 1990, Segal described an algorithm for constructing such an
embedding when the polycyclic group is given by a finite presentation;
however, that algorithm is not suitable for computer implementation. We
describe an alternative algorithm for this problem. Our primary tool is a
program developed by Lo in 1996 in which the Gr\"{o}bner basis method from
commutative ring theory is extended to the group ring of a polycyclic group
given by a finite presentation. Preliminary experiments indicate that our
algorithm will be efficient enough to investigate some interesting examples.
Further experimentation is needed to determine the range of input for which
the algorithm is practical with current technology.

This work was undertaken as part of the author's Ph.D. thesis under the
direction of Charles Sims and was continued collaboratively with Eddie Lo.

\begin{center}
*******************************************************************
\end{center}

\smallskip\ 

\noindent \textbf{Deepak Parashar,} The Robert Gordon University

\noindent \textbf{Quantum Groups and Quantum Spaces }

\smallskip\ 

\noindent  

\begin{center}
*******************************************************************
\end{center}

\smallskip\ 

\noindent \textbf{F. Leon Pritchard, }Rutgers University-Newark

\noindent \textbf{The Ideal Membership Problem in Non-Commutative Polynomial
Rings}

\smallskip\ 

\noindent  Let $X$ be a non-commutative monoid with term order; let $R$ be a
commutative, unital ring; let $I$ be an ideal in the non-commutative
polynomial ring $R\langle X\rangle $; and let $f\in R\langle X\rangle $. In
this setting the problem of determining whether $f\in I$ is studied. In a
manner analogous to the commutative case, weak Gr\"{o}bner bases are defined
and their basic properties are studied. We will see that in the
non-commutative setting, when the coefficient ring is not a field, and when
we enlarge the polynomial ring by adding more variables, weak Gr\"{o}bner
bases may exhibit unpleasant behavior that has no analog in the commutative
case. Quite in general for $f\in R\langle X\rangle $, it is undecidable
whether $f\in I$. This follows from the fact that the word problem for free
semigroups is undecidable. If $I$ is generated by a recursively enumerable
set, then we give a semi-decision procedure that halts if and only if $f\in
I $. Finally we examine a class of nicely behaved ideals for which weak
Gr\"{o}bner bases can be easly computed.

\begin{center}
*******************************************************************
\end{center}

\vspace{.1in}\ 

\noindent \textbf{Mark Stankus, }California Polytechnic State University Of
San Luis Obispo

\noindent \textbf{Applying Noncommutative Gr\"{o}bner Basis to Problems in
Analysis and Control Theory}

\smallskip\ 

\noindent  There are a number of theorems in analysis and control theory
which have a major algebraic component. This algebraic component consists of
finding a system of matrix equations which has some desirable property
(e.g., amenable to numerical solution) and which is equivalent to a given
system of matrix equations.

Our experience has shown that transforming the given system of matrix
equations into one which has a desirable property cannot be done by using a
noncommutative Gr\"{o}bner Basis algorithm alone. One common concern is that
a noncommutative Gr\"{o}bner Basis can be infinite and so the noncommutative
Gr\"{o}bner Basis algorithm will never terminate. When one stops the
algorithm, a Gr\"{o}bner Basis is not obtained. Whether or not the set of
relations obtained is a Gr\"{o}bner Basis, many of the relations obtained
may be conceptually redundant from the perspective of the application being
considered. For this reason, we consider the following additional algorithm:

\vspace{.05in}

(1) Find a minimal generating set for an ideal (so that one can remove
conceptually redundant information generated by the Gr\"{o}bner Basis
algorithm).

\vspace{.05in}

\noindent Since allowing for changes of variables can be very useful, we
also consider the following additional algorithm which facilitates the
introduction of new variables:

\vspace{.05in}

(2) Compute decompositions of a matrix expression into a composition of
matrix expressions which respect certain qualitative information.

\vspace{.05in}

Our methodology for deriving the algebraic component of a theorem uses the
noncommutative Gr\"{o}bner Basis algorithm and the two algorithms mentioned
above. The methodology consists of running these three algorithms on a
computer for a finite amount of time, displaying the relations obtained,
having a person view the relations obtained, making any desired conclusions
based on the non-algebraic components of the theorem, making any desired
changes of variables and repeating the process as necessary.

\begin{center}
*******************************************************************
\end{center}

\vspace{.1in}

\noindent \textbf{Victor Ufnarovski,} Lund University\ 

\noindent  \textbf{BERGMAN and ANICK - programs for non-commutative algebras}

\smallskip\ 

\noindent  The last versions of two Computer Algebra programs are discussed.
One of them (author - J.Backelin, Stokholm University) is a rather efficient
program for calculating Gr\"{o}bner bases for graded algebras. Another one
(authors - A.Podoplelov, V.Ufnarovski, Institute of Mathematics, Moldova;
LTH, Lund, Sweden) calculates Anick's resolution.

\smallskip 

*******************************************************************

\noindent \textbf{John J. Wavrik, }University of California-San Diego

\noindent \textbf{Gr\"{o}bner Bases, Rewrite Rules, and Matrix Expressions}

\smallskip\ 

\noindent This talk concerns the automated simplification of expressions
which involve non-commuting variables. The technology has been applied to
the simplification of matrix and operator theory expressions which arise in
engineering applications. The non-commutative variant of the Gr\"{o}bner
Basis Algorithm is used to generate rewrite rules. We will also look at the
phenomenon of infinite bases and implications for automated theorem proving.

\begin{center}
*******************************************************************
\end{center}

\vspace{.1in}

\noindent \textbf{Sergey Yuzvinsky,} University of Oregon

\noindent \textbf{Koszul algebras related to hyperplane arrangements and
graphs}

\smallskip\ 

\noindent In the talk, we discuss the Orlik-Solomon algebras. Such an
algebra $A$ is a combinatorial interpretation of the cohomology algebra of
the complement of a complex hyperplane arrangement. $A$ has a standard, so
called ``broken circuit'' basis. For the well-studied class of supersolvable
arrangements this basis has a very nice property that allows us to deform $A$
to a monomial algebra $A_0$ defined by a graph. Studying a basis of $A_0$ we
recover that it is Koszul (a theorem by Fr\"{o}berg) and obtain an elegant
formula for its Hilbert series. Then Drinfeld's deformation theory implies
that $A$ is Koszul.

\begin{center}
*******************************************************************
\end{center}

\end{document}

--=====================_853959217==_
Content-Type: application/mac-binhex40; name="ABSTRCTS.DVI"


(This file must be converted with BinHex 4.0)
:$%&#8e453e46,N4@53!r2cmr2cmr2`!!!!"@Y!!!!!$8SIF#!B15`"`l!!!!!!2
S'b"8C9JJEh9dF(9d)$%j16FZ-$%Z-$)k-6%`1BX!!!!"!!!!!!!!!!!!!!!!!!!
!!!!!!!!!!!!!!!!!!!!!!!!!!!!!rrrrrk!#SK&-MD$p2T(XS!+MEK50S2f"NHb
0NJ#HaE(c$d66lA3!%8HZ!"&(VJ!&Bfeb-6Hk3CB&0h4#Ne169*05Nd'63j08Ne1
1U4'!!+31J!#0N5@`K[-1@+Y4#`!-!!!!$!!!!!9MEA)a-VNU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSUMTmLZMQ0N4X!!2-3`YC1S!!-!!!!$!!!!!CME@*i-6+l4f9TFTB%J!"
"CfjKFR0cEfiXNlP9EQPfPDabCA*cDA56HCB$kUK[CT0$B@aTCQpbEQPKNf&dNd*
PFQZ3!+abC@aPHBkKMC%E!!#l6fk@")!!4T(qi!"eEQ0dD@pZB@acNf&ZC*02GA4
cD@4PNd0[FQjPFR16EfD66@pZEfeTB@b65@4PB@acMUDKMC%E!!#j6'9dPJ6*CI-
6Yq&RS`!-!!!!$!!!!!CME@eT-6+qDj%&-)+jBT!!8ijPNf'6$'9XC#bE"3%8[P+
4"1+[Z@'6CR*PCC1qDj!!Cafj,@&XCf9LFQ'6Efk6FfpYCC0cCA3XQ'&ZC*1q5C%
&ZZLjBC0dPDabGj0[,A0TC'9NPJ6*C@PNC@&XNfpQNlj5N!!C5VNZMU'0N4X!!&H
4r`9@CCB%qFThD@aXNh"bCA0PETUXFR56Fh81BfPPETKdNf0[EQ4TG'P[ER16Efk
6G'KPNfPNC@&XNlj*Q`AV6EPKEQ56G'KPNf&XCf9LFQ'6[P+4"4-8Z@C[FT1q5CL
jG'q1SBf4'`!!D''9V(*fNf@@!rV-BC--EQPdCC0LBA0TFj0[CT0QG@jMG'P[EQ&
XFj1q8T%$LKAc&L%L,*S!$!!!!!S!!!!'BfecH6%``5'4!h$,[QZ3!'FGZ5k4"@P
-9'KPFQ9LQUabHC0hQ'@6Cf9dNf'6Cf9ZCA*KE'PkBA4TEfk6EfD64Lj6,SkKMC%
E!!"0B@0KG@aKQUabH5GcPJ1C(R*PFh9XG*0QFQpYNc%j-6BXN31TEA4SBA56CAD
BCA*jNfPNC@&XNlj*N35+SEP[CT1qDj!!Cafj@ljBMCm"c-cc%Aal@3F!#!!!!!J
!!!!%Bfeb1,`aMT%%`!5q1if@!Irq1T-kNcU1N4(+R$Z4!Irq@)fI!Fc-ma6A!4F
b!!J!!!!)!!!!"@0YE@Ni[fk1N3@S8,PGNfKKFj0KN`aZDA4PNf*KFfPcMU'0N4X
!!'pQPJ6((@CeEQ0dD@pZB@acNljVQQFGZ9Zq@)fI!Fc-[$'1N36!",ilMCB"rri
kNcU61Sk4%FUF1j%"rrjBMCm"c-brESk4"DK3Z9f@"-b4`5'6[QZBZ5k4"mj!5@k
@"-FGG'KTFj0MBA0PNhHDV(*PNfGPG*0YEh*PEjKfQ'9bNh4SBA56D@D6[NQ4"EL
JZ@KKFj0KMU'0N4X!!%GbIj(k)!4[BQjPFTB%hX*LBA0TFj0MEfjcDA0dD@jRNfp
QNlj`NlPPE'9YC@kDV(*dFbb4"4[)G'KPET0dD'@6ETKeECKLN!"6MQ9bNfpQNfC
eEQ0dD@pZB@acNfPZNh0eBjKSMU'0N4X!!''@"*`#BQ&cDA16DA-XQ`6)@'C[FT-
-H'9NNljZZ5bBBT!!8ij[G@jNC@56BT!!V(*jNf'6!LLqF)fIqk8b[&ZrEMfm-Pf
1N4,K3,NT,@CeEQ0dD@pZ,T%(61e8D'PcNfCeEQ0dD@pZNfPcNf0XEh0PE(Q1SBf
4'`!!FQ9XBA4PC*B&'MpdEj0dD'@6E@&iD@eKE*0ZPDabG@f6BT!!8ijPFTB&'Mp
[CT0MEh*ZCA*cNfpQNf'6E@pZEfeTB@b6D@4PB@b6Cf9ZCA*KG'9NNf+3!+abHC1
qF)kKMC%E!!#jE@pZEfeTB@acPJ2UU'PZNljZNlPfNIpBj'&bD@&LE'9c,SkI'i!
!MC%PX)BU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSUMTmLZMQKMC%E!!#l6@PVN!#J!'@@")!
!3Q&bC(TPE'`XNlP6B@aTFf*eFRQ@!qUS8h4KG'@69@jTGT@XFQ9bFfPdNhQ1SBf
4'`!!Zd'@")!!6'PQG'9NNdGbIj(j3!"[BQjPFT0#BA0TFj0QEh+6G'KPNd9ZPD!
!GT0PE'p`D@jRN35!!%&XCf9LFQ'1TU'0N4X!!,P*ETB#lh0dD'PcNh4KE'Z6GjU
XFQ@6BfpZFfPNCA+6BC--EQPdC5eND@ePER0TEfjKE*0aG@pdD@9ZQ(56EfD6BC0
`BA4SNf&XCf9LFQ'6B@jNNf4PE@pZ,BkKMC%E!!"cG(*KG'@@!rP-D'qDV(*hNfP
dFj0PETKfQ'9XEh"TEQH6B@aRC@*bBC0MB@k6BTT6MQ@6E@qBC'9XC@56Efk6BC0
MEfe`GA4PFT0QEh+6D'pYEfa[CfPMB@b1SBf4'`!!Bf&XBh9XBA4TEfjc,T%%eF9
"N3,"#fePG'K[N!"6MQ5@!X&AEfD6E'PQG'PZCj0KNh*PC(9MC@564h*rNISJ"'p
LEQ9bNf*KFfPcNfCbEff6G'KPNfpbD@GTEQ&XNf&XCf9LFQ'1SBf4'`!!G'q@!qU
SDA4cNf9ZPDabGT0PE'p`D@jRPJ2UU'&XCf9LFQ'6DA16B@acEj0`FQ9cC@k3!+a
bG'9N,SkI'i!!MC%PX)BU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSUMTmLZMQKMC%E!!#l6'P
ND@'@")!!4QPXGA-XNlP1Eh*dD'9KFh4PFQk@!qUS5@aXD@j[DA169@jTGT@XFQ9
bFfPdNhQ1SBf4'`!!ZeGSN!#J!(Q@!i$24h*rNIP!!'pLEQ9bNd*KFf9c2j%&U["
$Efe`BA*TFfpZNfpQNh0[E@@6E@9dD'q3!'!!C(16CQpbNh0[E(CTEQH6FhPcG'9
YFikKMC%E!!"[CTB%J!"ZEfjXD@jPBA+6CA&eBA4TEfjcMUDKMC%E!!#j3fpYF'&
bDA0[ER1@!dkHGfPdD*0cEfePNfpQNh4SCC--H'9NNh#D8ij[D@k3!+abG*0KE'G
[FQPdD'ecNhGTE'b6BTKPNf4TFf0eFh0PC#k4"36G8A9PFh4TEfjcMU'0N4X!!(*
PCf&bC'PZCjB%QTK`QP11Eh0cD@*TE'PdD@9cNh4[Nf&`F'ajNdGbIj(k)!4[BQj
PFT0#BA0PFj0TC'9KFj0dEj0dD'9cCC0KE'G[FQPdD'ecNhGTE'b6BTKPMU'0N4X
!!(*KDA0PC#k1TTmEJ!#0N5@`KLSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LU1MSk-L`!!!!)
!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!US!+L%8b0S2d
qNHbJ!U0Z&)fJrB'4l+31J!#0N4X!!,Y8NIlJ!'&dD@&ZBCX%J!"(BA4PGTEr3!"
K,8PfNf&ZEj!!S!"fNf%XQ,P"E@9bD@0KETX$kUK9EQPfPDabCA*cDA56HCKTETK
#G@aRBA*TBBkKMC%E!!#l6QpZBfpYEC@J!(9dBA4TGT0PPJ5!!%GbIj(j3!"[BQj
PFT0#BA0PFj0TET06Dj!!S!"PGbe`N!"J!'pXH@j[E@PKE*05D@jRFikT%@p"SBf
4'`!!Z9H4r`9@CCB$jITcG(9NHC0KNf0XBA0cNfpQNfGbB@4PC*0cG'&ZC'&bC*-
-EQPdC@ajNh"bCA0PETUXFR4PC*0aG@&NFQ&dD@16B@aRC@*bBA16[N'6Z@qBGTK
PFSkKMC%E!!"KPJAFG3aiC@56$'9XC*1q5j%!h*kj,*%'@1PMB@aXC@56BQPZEfe
TB@b6FfZDV(*PGj0`N!"6MQpXH@j[E@PKE*0bD@jRFbk4#`j)4T(r"9C[E'a[Q(G
TEQH6BC0ME'&cFfPMB@b1SBf4'`!!G(*KC'PdD@pZPJ5#abKKEQ56FQ9MC@kDV(*
dNh4bC@jN+5b4"+M2GjKPNh4KDjKPNf'6BfpYQ'*TEQ&dEh*TB@b6BA"`FQpKBjK
SNh4[Nh0dG@4jNh4SCC0KE#f1SBf4'`!!Cf9LFQ&TBjB%qNe`FQp`QP11CA*dD@9
cNfpQNlj"Z5k4#'I26h9bNh"eFR#BEh0PNfPcNh4[Nf9iD'PLDA56BC0ME'&cFj0
[CT0ZEfiYBfpYEC@XFR9dBA4TGT0PMU'0N4X!!'&XCf9LFQ&cPJ0Id(GTG'L6Cfq
98ij[Nf5@!er3B@aRC@*bB@PMNh"bEh#D8ijPFR4TCA16B@e[EQH6GfKTBj!!V(*
SNdj[Q'9dD'9bD@&ZEQ9cFbb4!hZ9BTKPD@jRNf'6C'mYMU'0N4X!!'eKD@iXPJ8
lh(*PCh9XBA*TG*UXFRQ4r`9@,*0hD'PMQ'L@"2KVBf&ZNf+3!&11CC0bC@&NNfm
,Nf'6F(*PFf9ZQ(4KG'P[ET1q3CB&)(fj2C1q5if0N3,FR-&SMT%(KdHq@)f4!2'
$`@Q1MT%Bipqq2ENS[ND4!D('Z5NXN38lh(GSCA*PMU'0N4X!!,jBN35N),NpMBf
4!l+G`@D1N3QbRVjiMCm"c-bm-Bk4"-!%[MZ@!Irq1MSk1j0iMCm"c-brESk0N3@
S8-&RMSk42qM(Z@PcPJ3KH''6Ff9dNfpQNfPZC'9dCA*YD@jKG'9cNfpQNf4PCh*
PCC-a,*%%,bbq5if0N3,FR-&SMT%(KdHq@)f4!2'$`@Q1MT%E"9QjDA16G'KPNh9
ZDA4KFRQ6CR*PCBkKMC%E!!"KFh0[N!"6MQ0TBA4TGTUXFQ@@"%$1B@aRC@*bBC0
RC@jPFQ&dC@56BTKjNljBN38b8EPKEQ56+,j'N3'KaVNTNfPcNh4SCC0dQ(HBEbe
cD@4PC*0TC'9KE#b4"&CACf9ZCA*KG'9NNf+BHBkKMC%E!!"KPJ2UU!aZDA4PNh0
PG*0[CT0SEfe[Cf9ZC@peFj0`N!"6MQpXH@j[E@PKE(-ZMU'0N5bIp%D4r`9@Efa
XEj!!V(*hD@jRPJ4rGPXbA5b4"+5UBC1lBQPZEfeTB@b@"5ViFfZ3!+!!CAH6F*!
!B!"[E(PZEfeTB@b6FQPZCj%%VhDjDA1@"(pfBC0RFQ&NC@56B@aRC@*bBC1q3C%
%8TZj2BkKMC%E!!#q5if0N3,FR-&SMT%(KdHq@)f4!2'$`@Q1MT%Bipqq2ENS[ND
4!D('Z5NXN3ESYAGSD@13!+abD*B'6hpSBA16F(*PBfPcC@ajNljZZ5LqETB%5qM
"!*1j-5Qq2ENbPJC2If4P$'jTEQH6FQ9XBA4TEfjcNlj'N3N+1ENpN3GSFm&Q[RL
0R`(-c,pUMT%%CJUqH)fI!Fc-[fQ1N3H``X%!MU'0N4X!!,jMMCm"c-brD@U1N3G
+j,jeMCm"c-brD@U1MBf4#8VL`@U1MT%2dfQj-CB$A9l"&*1qDC-mNfU4"!Sa`45
6[Ql"ClilPJ2[BVPcG@1DV(*SNh4SBA56+'%TNljMMCm"c-brD@U1N3Xk4VPKFQ@
6EQpZ,ATPFQq6Bfq3!&11C3jMD@9ZQ(4c1j%$mEmSBLQ6[R@0R`(-c,pTDSk4#UK
#Z6f4!eeH[RL0R`(-c,pTMCrpZ16c'('K*3X!"J!!!!B!!!!&BfecH6E$-)k1N3B
@SEjiMCm"c-brDSf3!(B)Rrfij--`MSk4"aI4[MZ1SBf4'`!!Z@C[FTX%8cXaPJ3
(8X%8NljTNcb6DT%%Y#A"&*1qEVNXN34YB(GTG'LB[QQ0RrZP-[-A[N[)#`!)!!!
!#!!!!!9MEA0j1-)`MTX'eBZq2*0UN3#XdlNXN34YB,jTMCrlT6,#-)kB[Mb6DSf
4!+c6RrZP-X)`MT%$H`bj1j%%Ki8SBbQ@"&-lG'KPNh0PG*1q4T%&p3'jDA16BC0
bC@4eBf9NNdGbIj(k)!4[BQjPFT0LBA0TFikKMC%E!!!SGbjb,R3ZN38ii(4SCCB
$kUKNC@FYE'9iNfpbC'9bD@jRNfpZNh4SCC0QFQ9PNh0PE@PRFQpeF)f0Nm&SMT%
)P91q@)f4!2'$`@Q1MT%AmHfj+C0[CT0dD'@6D@4PB@b6+,j'N3'KaVNT,SkKMC%
XRr4ANIm&9Q@@!c%)CfPfQUabCC0ZC@0PFh0KFRQ6B@jNNh0e$Q0TC@kBG*0MEfj
NDA4TEfk6CQpbNdj[N!"6MQ9dD'9bD@&ZEQ9cFj0[CT1q3C1jD@k6Bf&cCC0dD'&
dMU'0N4X!!(4SCCB%LN4cCA56EfD6FQ9XBA4TEfjcNlj'N3BX#VPTFj0cFA9KFQ8
YCR*PC5k4"aHe9j(r"9CPNh0SEj!!V(*hNh4SBA56G'KPNfj[G'P[ET0[CT0(FRq
4qL!%Ef*ZCA+6BQ&cDA11SBf4'`!!Bf&ZPJ0-$@+D8ijPNf9iG'9ZC'9NNfC[FT0
YEjKNG@aPFj0[PDabGT0PFTB$6!ecG(*TBh4XHC0[FQ4PFQ9NNf&XCf9LFQ&c,*%
$Dm9cEj0dD'&dNf&ZNf&ZB@a[Ch9PNfpQMU'0N4X!!%*PFQGYB@iRFjB#ccY%D@&
YEfjNNdaPE@eKNfK[E'4cNbKMCLk4"0TQ@c*G,*%$"qSb,M)TNf&ZC*0KF("XHC0
dD'PcNfC[FT01Ej!!8ijPG'KPFQPKET0cDj!!V(*PGikKMC%E!!"`QP11EfajEQp
YD@&XPJ4Z4R*TEQGcNhGTG'L6BQPZEfeTB@b6FQ9XBA4TEfjc,T%'`lT8D'@6CQp
XE'q3!+abGfPZCj0bCA0eE(56Bf&ZNf+BCC0PH(4bB@0dC@51SBf4'`!!CR*[ECB
$kUKE-Pf6B@jNNeXcA5k1TU'0N4X!!,Y8D'9[FQ9YN325+I-FQlZ)3!!-!!!!$!!
!!!CMEA4T-6,(6*[rCQCPG*%%pQfq3CB$99+j2C1q5if0N3,FR-&SMT%(KdHq@)f
4!2'$`@Q1MT%Bipqq2ENS[ND4!D('Z5NXN31@-FGLQ'@@!p)TBC0LD@j[E@PKE*0
cDf9h,A#BEfajEQpYD@&XNh*TEQFZN39'%&0eF(#BEh0PNh4SCBkKMC%E!!"cCA5
@"$-eEfD6FT[rCQCPE'&dD@pZFj%%k)@q4T%&e2[(DA16Fh&eBA+BC5eQFTKPQ'8
ZN39QD94SC@k6G'KPNfC[E*%!QCPXEhGTEQH6BjK[EQ4TG'P[ER16BA+BCC0PQ(&
eDACKE'9ZG$U1RaVk"if4*9rm+$%TN3@b*'@ErfCQB@0SPJBNSVjiMCm"c-brDBk
4!f6D[RL0R`(-c,pUMT%%CJUq1j%&Drh(GfPdD*1j-CB&Q)M"&*1qDC-mNfU4"N9
E`456[Qkj,*%&P!6(BA"`Q'@BBA*cPJ9Vr@PZNh4SCC0bD@GSG*0SB@jNNh0TC'@
6EfD6FfpYCBkKMC%iAqabNIpQCQ9XBA4TEfk4"$-eD@k4"0"B[ND4!D('Z6Z1T"K
HJSf4*9rmabJb+C%%AGUq3C%$kUM(DA1@"$-eE'9QG*01Ej(rCQCPG'KPFQPKEMZ
1SBf4*9rm+$-TN34GfVj"N32UU-GTFjB%-c9bD@GSG*01Ej(rCQCPG'KPFQPKEMZ
1SBf4*9rm+$3TPJ2ibN'3!,-bERQ6E'9QG*0TC'@ErfCQB@b6EfD4"S&6[N'6afK
KFj0KN`aZDA4PNdGbIj(jrre[BQjPFT0LQ'&cDA16+(GTG'L6FTKPFh#BCCKMG*0
dEj0cEfePNfGbQ'&ND@jRMUN1J!#0N6KIl'pQN3Cc-Ej"acXTMU'0N59Ir#Je+CB
$G`a"N!#c-QjjNh*TCfKdNfPNCC[rCQCKE*0[CT%&rj@q3C%$(I2(D'&cNf'6$'j
TG'@64h*rNIRrr@pLEQ9bNf+BBA0TFj-SGfPdD*0bQ'9cF*KPQ'0dNh4[Nh0[E@@
6Ch+BB@4TEQH1TSf41&rXEfD4"VZq[N'j1j%$kUM(4T(r'CPeFR4SCA*YEh+ErfC
QC5b@"$-eB@jjNfpQNh4SCC0MQ'pZC'PdD@pZFj-S-5Q6,C-S05Q6D@e`E'PPFj0
dD'&dMU'0N59Ir#KK+CB%ah&dD'@6E@9YBT[rCQCPFR0SDA#6F(+BEf*XC@f6CQp
bN`aZDA4PE(Q6Cf9ZCA+BBA4PQ'56EfjP,A0TC'@BC*0TC'@BB@acNfPZN3@Y)Ej
"N35,lFGTFj0NC5f1TSf41&rXBfPNB@*XC6Z1SBf4*9rm+')TN35QClj"N32UU-G
TFjB%-c9KNf4[E@&TEMZ1SBf4*9rm+'-TN34GfVj"N32UU-GTFjX%-c9bP[pQCQ@
6Ch9XBA+BD@kBG'KPQ(0PER0PQ'pQQ%'3!,-bFR4TELe6BfKPE(4PFTJSBfBZ@c*
G+5k1MTmH!!#0NJ$RN!!#Z6+1MSb,!!!!!`!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
!!!!!!!!!!!!!!!!!!!!!#RHJ!U)46)fJr6k4l+!#Sfi8MD$pJC(XMC%PArc(+'3
TPJ5Jbh4SCC0[F*ErCQCPFT0KG'pbQ`5JbfpZN39(NEjBMC%!mB1Iqk8b[$+1N3S
6D-GZBA4eFT0KE*%!QCPXHCKNC3aZCC0NQ'*jQ(4SCCKaG@&NFT0KG'PMQ(+6C@a
KG'P[ER14"CkS[ND4"J1Rah0KG'Pc$'9cMU31J!#0N6KIl(4SCCX%-c9cCA4SCCE
rCQC[FT0PG'PMQ&Q4raQCB@jRQ%*KH(4PFTKPNh&eBA4TEfjc,SkI*"9@MC%E!!$
c(X,@6U!!$QCQ!!`!!!!'BfeLH$%bb9*PCQ9bC@jMCA11RaTL)if0MC%E!!#j@c&
GMSk4,8F365k@"1Ec3A*dD@iXQ`8Q"PFZNe0MN!#XFQKPE(4PFLbB4h*KC'9NNf&
XCf9LFQ&cNfpQNfGXEf*KE*0ND@ePER0TEfk6-bbBad'@rfCQC(CKEQ16CA14"4X
EEfD1SBf4,8F36@&dD#k@!qUSZcBfNlNS-6Ni0bNXNc%h-5db-6BZMU3BJ!#0MBf
4'`!!@c*GMSk4,8F39#kE!qUS4f&dCAD@reMNB5e*GT0KEQq3!+abGT0K,*K6Dj!
!V(*PGjK`N!"6MQpXH@j[E@PKE*KbD@jRFbbBadSZPJ3c08'3!,-bE'GPBR+4rfC
QB5b6Zc%i0CLj+$%j16BT,*Jh-6!Y0c8c,SkKMBf0N4X!!&XcABk1N5e(%&3ZQ`2
UU%GKG'9fP[pBj'%Y5AD6B@j[N!#XFRD6B5bB65kB9T(r"9CKETKNC@kB3Q9bCfJ
XQ&0PE@PRFQpeF(1BEfDB55edN!#XFRP`N!"6MQ@Bae"bNIpQCQ9`FQPZG#k1U4Z
!!)f4*E#'Z5SU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LU1Rb+k1D31J!#0N4X!!,Y6GA0KET%
%J!")CA*YD@aXCA)XPJ2UU,P1CAH66@9iD@0[Ne0dBA4PNe9ZDAD9V(*PFR0TG*0
jMU'0N4X!!,Y5CAGbDA4TEQH@")!!FhPcG'9YFj0KEQ56-beYB@jTCQpXC(11Ra'
!!+'0N4X!!,P8D'@@!rL*CR9ZC'&YC@k3!+abG'&XNfGbEh9`Fj0[CT0YEh0dNbK
MEfjUC@0dGA*KE'ajNIm&9Lb4!r`"B@aX+C0ME'pcC@56-beYB@jTCQpXC(16GfP
dD*0eEQNYMU'0N4X!!'C[FQf@!kQ#Cf9[E@9dFQPPFj0SBC@XFRD6CCB$UB)-EQP
dCC0MEfe`E'9dCC0bCAGbDA4TEQH6FhPcG'9YFbk4"5-T9'KPNfCeEQ4KE@9ZN!#
XFR4KE*0RFQpeF(11SBf4'`!!EfD@"#iTBC0XBA*RCC0ME'&cFj0[CT0KE@&XCf&
YFj0[CT0MDA*ME'@6BR9ZC'aPFj0KE(0[NfKKPDabGT0PPJ3Z+3aZDA4PNf0[EA"
XCA4PNh*PGh*TG'PZCikKMC%E!!"cHA0dC@ec,TX&11"8D'@@!qUSCf9ZCA*KE*0
MBA0PNh*PE@&TER16Eh#3!&11C@iZQ&4SDA16DA16DQpTETUXFR56GjK[FQZ6GfP
dD*00D@ZBCC06D'&`DA*[,SkQMC%PX)BU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSUMUD0N4X
!!,Y"EQjPPJ5!!%KPHAH3!+!!Eh*dD#b6Z99ZDAD9V(*PFR0TG*0jPJ2UU'pQNeH
4r`9@B@aPFikKMC%E!!#l3fpYF(9dCA*TFf9NPJ5!!'aPCR565fkDS!"eG'JY3Q9
ZC'PiNh"bEj!!B!"MC@4eFQ@6CQpbNf9ZQ(9YCA*KG'PZCj0MEh0PG(11Ra'!!+'
0N4X!!,P9FfPZCjB#[H*dD'@6F(*PFf9ZN!#XFR4KG'P[ESf6[Mb1PJ[KDVPB,&+
0[Mk1NlP[CTB#[H*KNfGbEh9`NdFXNf&ZC*0dD'@6Cf9ZCA*KG'pbFj0[CT0KNh0
eBQGbEh9`NdL4!Vf9D@k1SBf4'`!!4bb@!f`#B@jNNf'6E@pZEfeTB@b6Eh*NCA*
TEQH6Efk64LKB+C%$Dq*[EQ@6Bf&ZNf4[Nf'6E'9QG*0,ET!!V(*eG'JY3Q9ZC'P
iNf0[EA"XCA4TEfiZMU'0N4X!!&4SDA1@"#p1CfPfQUabCA16BC0FE'9QG#eMEfe
`E'9dC5+6FhPcG'9YNh4SBA56Bf&ZNf+3!&11CC0KF("XD@9NNh4[Nh4SCC0hQ'p
bC(16D@k6G'KPNfCbC@@1SBf4'`!!Ch*[GA#@"6SP4LKB+C%&1FjdEj0PETUXFR9
YCA*KG'@6G'KPNh*TCfLBG*0MEh0PG(16EfD65*X&1FjTET0(,T0*Q'KKPDabGT0
PPJ8k*@0[EA"eG'9bDA0PC*0dD'@1SBf4'`!!F(*[QP11Bf9cFjB$kUJSGA0TEQH
63AKTEfdT,T%&11"*G*0TFj0KNhD4reMNB@aTC*0KE(4PFQjKG'PfN!#XFQ@6G'q
6G'KPNe54r`9@EjKNC#e$Ej!!V(*iCA4PFT0`FQqBBf9cFbk1TSf4*E#'+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+SkI)VSjSBf4'`!!ZeKPEQPKN35!!%YbB@ePFLb@!qUSZ8j
PGj00CAKTBfq68h4KG'@69@jTGT@XFQ9bFfPdNhQ1SBf4'`!!Ze4SCCB%J!"1EjT
J!'9dD'9bD@&ZNe"bEh#BCA*dN!#J!(Q6D@k68fpYCC04G@&NFQ&dD@163@aRC@*
bBA11Ra'!!+'0N4X!!,PANIm&9Q@@!kXaD@kDV(*dFQq3!&11C(9MCC0KNfjPGj0
ME'&cFj0[CT0ZEfjMEfeYQ(9dBA4TGTKPNh*TEQGcNf0KE'aPC*2(F(0PG@4[F*(
rCQC[E(PZEfeTB@b4!rMIFQPZCh11SBf4'`!!Z@&ZC*B$Da0RDADDV(*PNh0e$Q0
TC@kBG*0MEfjNDA4TEfjcNfC[FT0cG@1BD*0KNh*TEQH6G'q6BTT6MQ@66QqBCA4
SCA*TB@iZN381@9"cCA9NEh#BEfajEQpYD@&XMU'0N4X!!(*TEQGcPJ0Th'&bCC0
cG'&ZC'&bC*--EQPdC@ajNh"bCA0PETUXFR4PC*0KE'GPBR*KFj0[Q(DBCA+6BC-
-C@aNNhGTG'L6FfpYCC0KC'4TG'P[EQ&XNh*P,BkKMC%E!!"cG(*TBh4TEfjcPJ3
B2QpZNh4SC@PbNf4P$'jTEQH6FQ9XBA4TEfjcI'jKE@9XHC0dD'&dNh4SCC0`N!"
6MQpXH@j[E@PKE(16D@k6BC0(FRq4qL!%Ef*ZCA+1MTmH!!#0NJ$RN!!#-ik1M)X
!!!!%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!C'U!#SK&
-MD$p2T(XS!+MEK50S2f"NHb0N4X!!,PLBA0TFjB$cq4QEh+6G'KPNfPNC@&XNfp
QNh*PE'&dD@pZFj0YN!#XFR9cG*0LN!"6MQ@6D'pYEfGPEQ9[GA16EfD6C'9RFQ9
PNc*mB@jNNfpZNh4SCC09CLf1T!k!!)f4'`!!EQ&bEj!!V(*fFfYTDCB$i"aRFQ&
`D*-!+,j"Z5NZN38eA&4SCC0ME'&cFj0[CT0`Ff9eC'p`QP11EfajEQpYD@&XNh*
TEQGcNh"bEh#BCA*XHC0TEQ0XG@4PFj0dD'@1SBf4'`!!Cf9ZCA*KE'PkC@5@"$m
cFfZDV(*PGj0`N!"6MQpXH@j[E@PKE*0bD@jRFj0TETKdFQq3!&11C(9MC@56BTK
jNddZNd&bG'PZNf&ZC*0A,T06BjKSC@adCA)ZN3BfJ&H4r`9@CBkKMC%E!!"eFf@
@!YISG'KPNfGbBA"SN`!S[N'j+C0dEj0NC3aZCC0KNhH9V(*PB@Z6CA+@!YISEQp
dD@pZNfpQNf&XE@pcG*0MEfeYPDabGA4KG'PfNf8XN3-1fhGSD@16D*X#eqKhNf@
BBf&XE)kKMC%E!!$(B@aYEh0dPJ3"M@14rfCQEfeYGA4KG'PfCC0[ET0MH@0XCA-
ZN38QhVPANIm&9Q@@!l5LFfK[N!#XFRH6BA16Eh9bNfeKD@k6FQ9cG@adNh4SBA5
6BC0`Ff9eC'p`N!"6MQpXH@j[,BkKMC%E!!"YD@&XPJ-1+A*TEQH6GfKTBjUXFQL
6DA16B@aYEh0dNf0[E@fBGA4KG'PfQ'@6Efk6BhPME'9cNfPcNdj[N!"6MQ9dD'9
bD@&Z,T%%lf""N3-0m@0[G@kBG'9bCAKKEA"XCBkKMC%E!!"cD'q3!+abGh1@!j5
jG'KKG*0KNdj[QP11CA4SCA*TB@k6F(0PG@4[F*K[E(PZEfeTB@b6FQPZCj0ZC@9
NNfj[G*0LQ'@6B@aYEh0dNf0[E@f9V(*eG'&dDAD6CBkKMC%E!!"[ET%$kUKMH@0
XCA-ZMTm9ZMQKMC%E!!#l@'9ZD@'4")!!5h*KE@9b,*B$kULj6Q9hNdePH'PMEj0
6G'&dCC09EQPfPDabCA*cDA56HBkKMC%E!!#l3fpYPD!!BQPZBA4[FQPKE*X%J!"
)Efe[G'p`NhQBEfDB8fPYF'aTBfPKE*K$Efe`E'9iCA11U4&BYU'0N4X!!,P$Eff
9V(*LD@jKG'pbD@&XQ`B9lfK[E@pdEh#6HCKTFjKKETKKEQ&XEfHBEfDBG'KPQ(9
cG@&XQ'K[E@pdEh#6HCKdD'9[FRQBEfDBB@aRC5f1SBf4'`!!BR*KD@1@"&4#G'p
`N!"6MQpXEfGjNhGSD@1DV(*SNfPcNfPZQ(4PEQ4PC*0dEj0bC3ePBh56BfpYQ'*
TEQ&dEh*TB@b6CQ9KG(9bCA16EfD6BC0cD@e`E'PMD@&XMU'0N4X!!'0[EA"XCAJ
ZN3L[-e4SCCB&%KPMEffDV(*LD@jKG'pbD@&XNhDBCA*cD@pZNfpQNf'6F'&dD*0
TFj0KN`aZDA4PNh0PFA9PEQ0PNfpQNh0TEA"XD@0PFikKMC%E!!#q'ifI!Fc-[$'
1PJ6!",ilQ`(rrKZ0R`(-c,`bMT1q1ifB1TJkQ$U1N4(+R$ZB'ifI!Fc-[fk1N3R
frEPTETB%6UeKNf0[EA"XCAL6!C0hD'9bCC0QEh+6-CB$rj("&*1qDC-mNfkj,*%
%CkjdD'@@"%kYC'PYC@jcD@pZNfpQNliEMCm"c-brDBk4"P1E`9b4!Zl"[KZ0R`(
-c,pT[#XaMT%5N!!$Z@PcMU'0N4X!!'&dPJ1ckfaPBA0dNljaQQijZ5b4!llGCQp
bNh0[E@@6F(*PGQP[GA0XHC0cCA56GT(r@14KE(9PNljaQ,NZN38QS94hN!#XFQq
6F'&dD(16BA*PNfK[E@pdEh"TBj0TET0dD'PcNf0[E5f1SBf4'`!!BQPZBA4[FQP
KE*B$kJKcC@jcCC0TCT0[EQ@6Bf&ZNf+3!&11CC0NC@C[FQePC*0dEj0dD'@6Eh4
SCA+6GfKTE'@6Dj!!V(*PCA"TEQH6G'KPNf4TE@9ZFfP[ESkKMC%E!!"[CTB$kUK
dD'@6D@kDV(*dCA*cC@0dD@pZNfpQNf&NDQ&MC@kBG*0cD@e`E'PMCA16BA56E'9
KFh56[R'3!'ijZ5k1TU'0N4X!!&4SCCB$M6pYEh4TGT(r@14KG'P[ET0QEh+6G'K
PNh0dG@4jNfpQNf0[ECUXFQ*TEQ&dEh*TB@b6D'pYEh4[F*KjNf0[E@9cNfCbEff
6G'KPNf&ZB@ajFfPcMU'0N4X!!'pQPJ,f'f0[EA"XCAL6D@jQEh*YBA4TEfk6FhP
cG'9YFbk4"1GF9'KPN`e[QUabGj0[CT0dFQ%1Bj0TET0cG@1BD*0KNh0jFh4PEC0
TFj0MEfjcG(*KD@jPC)kKMC%E!!"LQUabHCB$MhGdD'@6G@jNCA*XH@PZCj0cG(*
eBh4eFQ@6EfD6G'KPNh0jFh4PE6Z4!khGG'KKG*0TFbb4!k'dG'KPNf4jEQ&YD@1
6BT!!8ijPD''BGQP[FT0[CT0KNh0jFbf1SBf4'`!!G'9YPJ0IkfPcNfPZ$A9PEQ0
PC*0LQUabHC0TG(16Fh4KG'PMNh0dFR9MG(9bC5k4"3UK3fpYQ'*TEQ&dEh*TB@b
6D'pYEh4[F*KjNhHBBA16D@kBG(*[N!"6MQ4eBf9NMU'0N4X!!(4[PJ2UU'4PFf0
bD@+3!&11CC0QC@&dGA*PFj0[CT0dD'&dNh0dBA4TBj0cG(*eBh4eFQ8ZMUDKMC%
E!!"*ETB%%dGdD'PcNh4KE'XXN33GEhHDV(*PNhGTE'b6CQq3!&11Bh9cNfpZNh4
SCC0YBA4SC@eKG'PMFj0[CT0MEffBBQPZBA4[FQPKE*0SEfe[G'p`Q(Q4r`9@,T%
&XVj"CR4PFSkKMC%E!!"NC3aZD@jRPJ5pS@Pd,*%%mPphQUabCC0RDADBCC0KET0
KE'G[FQPdD'f6CQpbNf0[EA"eG'PZCj0TG*0hD'PMQ'L6GA0PFj0(FRq4qL!%Ef*
ZCA+6BQ&cCA16D@k1SBf4'`!!BCB&VHPQFQ9PNf&cFfq3!&11BfPKG'@6B@aRC@*
bB5k4#S+L9'KTFj0hQUabEh*VNhHBBA16C'pZCC0TET0MEfaXB@+3!&11Eh*KG'P
[ET0hDA4SNe*PD@jSBA*NMU'0N4X!!%aKG@+3!&11C@k9V(*LB@16D'9b,SkI'N@
bMC%P3)5l+VNU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LU1Rb&rkk'0N4X!!,Y3N!#J!'9dCA+
@")!!6@&XBfpXEA0[ELb6Z9H4r`9@BCUXFRPZCCB$kUK6G'&dCC09EQPfQ'9bFfP
dQ(Q1SBf4'`!!ZdGbIj(j3!"[BQjPFLe6D'PbFfK[QU!!GTB%J!"LBA0PFj0QEh+
6FA9KETKdG@f6C@kBGTKPE'p`D@jRNf&XCf9LFQ&cMUDKMC%E!!#j9j(r"9CPPJ0
R!QGTGTUXFQ@6BC0YCA4SEj!!8ijNNfC[FT--EQ4TEQH64h*rNISJ"'pLEQ9b,90
SDA*cD'qBGT0LBA0PFj0QEh+6G'KPNh&eB@kBG(9YNf9ZQ(DBC@a[F'PZCikKMC%
E!!"KE'GPBR*KFjB%EU&[CT0%FQPZCQ9X*f56B@jNNdTTEC@XFQ+3!&11Ebb4")q
IFfK[NhHE"'kKD'q6GjKdD'@BE@9dD'q98ijNFjKMB@kBBT0PQ'&`F'aTC@5BG'q
B5f&M,BkKMC%E!!"0Ej96MQq6C(Q@!kU3!'&XCf9LFQ&c,*%$Yf&KEQ56CAK`E'P
MDA4XHC--EQ56G'KPNf*KFf9cNfC[FT0aG@&ZQUabG(9YNf9ZQ(DBC@a[F'PZCj0
KE'GPBR*KFj0[CSkKMC%E!!"dQUabHA#3!&11CCB$kUK"NbKQEh+6G'KPNh&eB@k
BG'PkD@jRNf0[N!"6MQ81BfPPETKdNfj[G*0KET0PD@GSQ(4SNh*[N!"6MQpdNfp
QNh9ZDA5BH5NZMTmD4E+0N5@`KLSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LU1MTmH!!#0NJ$
RN!!#0)k1M)X!!!!&!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
!!!!MEU!#SK&-MD$p2T(XS!+MEK50S2f"NHbN$S!!MC%E!!#l4@4eBA*NEjB%J!"
NEj01BA0MD@ePET!!S!"dEj00BA*MEh-XNlP*688Y9903PJ2UU#K%CA"d,T%&11"
NCC00BA4PE@&dD@0K+C0#FQ&kD@b1SBf4'`!!ZdGbB@4PC*B%J!"5D@jRFj0[CT0
-Ej!!B!"MB@b64QPZDA4PNe*PF(*PFf9ZQU!!G'&dD@pZNe5BHA#3!'!!CBkT%86
hSBf4'`!!Z8GbB@4PC*B%,*C"FR4TET0KE'GPBR*KFj0hD'pcCC0MBA4PCfpbHC0
[CT0RFQ&NC@56E@qD8ijNG@aPFj0TFj0XEjKMB@aXHC0[CT--EQPdCC0bCA!YMU'
0N4X!!(*PFf9ZPDabG'&dD@pZQ`85QA56HA#3!&11CCKKFQ@BD@k6G(*[N!"6MQ4
eBf9N,T%)X,08D'@BFQ9`FQ9cC@k6G'&dD@pZQ(4SC@pbHCK[CTKcG@16D*KKE'G
PBR*KFjKTFikKMC%E!!"cG(9ND@9N,T%(F,T*ETB%Tr&dD'@6D'9bC@4TG'&bHC0
MBA0PNf&ZC*0TET0dD'@6Fh4KBQajNf9aG@PfNIpBj'&XC@k3!+abG*0dEj0SCA*
PC'PdBA*jNf0KFf8XMU'0N4X!!(0eBj!!V(*SPJ2UU'&XCf9LFQ&cNf&bCC0ME'&
cFfN-C@3ZMTmCTlQ0N5@`KLSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LU1RaaXX+'0N4X!!,Y
0D@Z3!+!!CC%%J!"1CAGYB@iXPJ2UU,P"GA0dFQ&XD@&ZNdjKG'P[EQ&XNe9ZDAD
9V(*PFR0TG*0jMU'0N4X!!,Y6EfePPJ5!!(9cCC0[CT0,ET!!S!"eG'JY3Q9ZC'P
iNfPZNh4SCC0cG(9NHC0[CT0RFQpeF(11TU'0N4X!!,P*N3,irRGTE'b@![NlC'9
cBh*TBT!!8ijPNh4SCC0eFf@6EfD65fkDV(*eG'JY3Q9ZC'PiNf&ZC*0[G'KPFT0
cEfCdQ(HBBA*PNfC[FT0`FQqBGQPZCj0dD'&dNf0PFR4KD@k1SBf4'`!!4@jRC@b
@!qUSCh*[GA"cNf&bCC0ZD@a`N!"6MQpdC@k3!+abG#k1RaQRZBf4*kAD+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+SkI)1(bMC%E!!#l4h*PG'13!+!!D'9ZPJ5!!%pcG'KPD@e
PFLb6Z954r`9@G@CdFj%$kUK9EQPfPDabCA*cDA56HBkKMC%E!!#l4QPZC'PZCjB
%J!"0BA4bDAL68Q9`FQ9cC@kDS!"dBA4TEfjcNfC[FT03Q'pXH@0jBfaTBj0(FQp
eF(11TU'0N4X!!,P*G*B&)ZGSBA16BTT6MQ9PET0VEQq3!+abGfk6FfPZBf@6G'K
PNc%j0M!RFj0dD'&dNf'6FfpXGT(r@14KBQaPNfGbEh9`Nlj(NlPMB@k6BTKPNf9
YN!#XFQ+BC@4NC@51SBf4'`!!D@k@")rP[NG-MBf4!IrqZ5L1N3D4`VjZ1j%"rrj
DMC%!h*kj+Bk1N56Km'C[FT0cEfePNljZNlPTCT0KEQ56EfjXHC0TCT1q4j1jDA1
6F*T6MQpXH@0jBfaTBbk4"bLA5@k6-6Nj-#b4",Nd8f9RB@b6C'9cBh*TBTKPC)k
KMC%E!!"KETB%l#eKE'G[FQPdD'f6CQpbNf0[ER0dFR9MG'PZCj0cG@1DV(*SNf&
ZNf9YQ'+D8ijPC'4TEQH6GfKPET0dD'@6F*K[E(PMH@0XD@16Ch*[GA#6DA11SBf
4'`!!CfPfPDabC@kE"-pLBT0jQ''B$'jTG'@BF(*PFf9ZNh4KG'P[EMZ4"8'rD'q
6Gj0PGT0PFLb4"3L4G'KKG*KKE'G[FQPdD'fBDA1BEQpdQ(0eDA4KBQaPQ'C[FTK
MEfdYMU'0N4X!!("eG'9bPJ9)m@PYF'aPE@9ZQUabG'&dD@pZ,T%*8laANIm&9Q@
6C'9cBh*TBT!!8ijPNf&ZNf&XG'9bEQ&dDADBCC0KE'G[FQPdD'f6CQpbNh4SDA1
6F(*[BQaPE5k1SBf4'`!!6h9bPJ6dR("bD@eKFRQ6G'qD8ij[E*0TFj0KNh"bEfG
bB@f6C'9fN!#XFQ9XEh#BC@56BTUXFRQ66'q6D@k6-6Nj0T0TET0hD'PMQ'L6G'K
PNdGbIj(k)!4[BQjPFSkKMC%E!!"LBA0TFjB%b[aYCA4SEj!!8ijNNfCbEff6Bfp
YEC@XFR9dBA4TGT0PPJ6+r(*TEQH6G'KPEh*jNfPcNf9iG'9ZC'9NNh4[Nh4SCC0
RFQpeF*0bD@jRNfpQNf'1SBf4'`!!F*!!8ij[E(PMH@0XD@1@!l5DCh*[GA#6CfP
fQUabC@k6BTKjNf'6$'jTG'@6F(*PFf9ZQ(4KG'P[ELk4"5EE8(*PE'PYD@jKFRQ
6CAK`N!"6MQ9bD@ePETKdFj0TEQ4TBf&dCBkKMC%E!!"dD'&dPJ3AIQpeFT0KE'G
[FQPdD'f6GfPXE*0LN!"6MQ@6C3jMD@9ZQUabG*0PEQpeCfL6G'q6D@kBGTKPFh4
TCf&dCC0cEfePNfPZQ(4PFQ9cG'PZCj0PH'&Y,BkKMC%E!!"`E'9c,T%%rf4'NIm
&9R9bG'KPFTB$2M9PH(#3!&11CA*TE@9ZQUabG'&dD@pZNfPcNfjPC@4PC*0dEj0
NCA4PFQeTEQ@6G'KPNh*KEQGPNfpQNfPZF(9dNfC[FT0hD'PMQ'L1SBf4'`!!G'K
PPJ2UU'&XCfpbDA4SEC0TFj0`FQ&MG'PMB@b6GfPdD*0MGA*bC@kDV(*dNh4PBjK
SEQpXEfGjNIm&9Lk1SBf4,*rd9'KTFjB&aP4hQUabEh*VNhHBBA16G@jNCA*dB@Z
BC@k6BA16F'&bG*0[CT0dD'@6BA9dD'pb*h168'JZ4#k6G'KPFfPcNh9ZC'9bNh4
SCBkKMC%E!!"NDA*PBh4TEfk@!qUSEfD63fKKFQaPFj06D@ecNf&ZC*0hQUabBA1
6BfpZQ(4TETKeC@56BfpXE'&LN!"6MQpbBA4TGTKPE(Q6GfPdD*0&C'4TCC0-Ebk
1RaQRZBf4*E#'+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+SkI('b`SBf4'`!!Zd4PCA"KDj%
%J!"3N!#J!'&bBA0SBA)XPJ2UU,P8D'@68QpLN!"6MQ9bG*0(Eh*NEfk69@jTGT@
XFQ9bFfPdNhQ1SBf4'`!!Ze&eB@kDS!"dG@f@")!!4h*[GA"cNf&ZC*04G@&ZQ(4
eEC06F'&MCA11TTmCTlQ0N5@`KVNU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSUMSkI(J!!MC)
!jj!!!M@1MSb,!!!!"J!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
!!!!!,qQJ!U)46)fJr6k4l+!#Sfi8MD$pJC(XT!k!!)f4'`!!ZdBZPJ5!!%aPEfk
68(*TG'13!+!!D'&bC#b6Z9*eG'GPFR14!qUS9@jTGT@XFQ9bFfPdNhNY6Q9hNf&
bDikKMC%E!!#l9'KPPJ-!!%PNC@&XNdePECUJ!'+3!'!!CA*cD'P`Ne"bEf*XC@f
6D@k66QpZ,80[E@fBGA4KG'PfQ'@68*K[E(PZEfeTB@b68QPZCh11U4%SXU'0N4X
!!,P-CA5@"%5J[PL4"6BMZ@+D8ijPNf'6EQpZ,@0[E@f9V(*eG'&dDAD6CCB%4+"
YEfj[D@56GfPdD*0dCA*YNfpbC'9b1j%%FCaXCA56[P+4"&hUZ@+BCC0KNf0[E@f
9V(*eG'&dDAD6C5b1SBf4'`!!G@jTG'&XPJ2Df(*TEQFlN32J(@aPG*1q5C%%c&Z
jBTT6MQ@6B@k6D@4PB@b6D@k6G'KPNfj[ELeMEfeYPDabGA4KG'PfNf@@!pVBF*K
[E(PZEfeTB@b6FQPZCj1q8T!!'8V"D,jBN3$aJm&TZ6Z4!q!GB@jNMU'0N4X!!'a
PG*B&Q&DqCTX(H+r"-T%'-,#q8T!!'8V"D,jBN3$aJm&TZ5k4#N(V5@k6G'KTFj0
cCA4dD@jRNh4SCC0`FQpLE'9YNfpQNf4PG'9bE@PZD@jRNhGSCA4SCA+6[QDB`6+
4"M#`[NQ4"SRCZ@PcMU'0N4X!!(0dG@4TC@3ZN3J-edPZPJ6EqQ'6E@&ZEQ9bNf&
ZB@a[CfpeFj0dEj0dD'@6BfpYEC@XFR9dBA4TGT0PQ`6EqQ0KFf8XN38B6hH6C@&
VQ%GbIj(k)!4[BQjPFTKLBA0PFikKMC%E!!"KFQ@@"*!!4f4P$'jPC*0KEQ56G'K
PDA+6BQ&cD@16F(*[F*!!8ijPFR4TCA16BA*PNh0dG@4TC@3ZN3FT[PH4r`9@CC0
hD@aXNh0PCC0dD'&dNfPZNh4SCC0ZEfiYMU'0N4X!!'0[E@f9V(*eG'&dDAD6CCB
$HTYcCA4dD@jR,*X$N34hD'9ZNh4SCC0MEj!!8ijP$Q0TC@k3!+abG*0bD@jRNfP
cNfj[G*0KN`aPE'3XQ'&ZC*0hD'9ZNhH3!+abCC0PEQaKFQGPMU'0N4X!!(4SCCB
%G6G`N!"6MQpXH@j[E@PKE*0bD@jRNf+DV(*jNf&NC'PZCj0YEh*PNhD4reMNBA*
TB@*XCA-XN35AfRHBC@&VNdGbIj(k)!4[BQjPFT0LBA0PFj0YBCKjNf9iD'PLDA5
1SBf4'`!!G@j`E'9KFf&ZPDabG*X$+N&LN!"6MQ9SBC0fD@pbQ(4SBA5BD'&cQ'j
[Q'&ZB@a[CjKTETKdD'@BBfpYEC0eG'&dDAD6CCKMBA0P,T%%q,j4G@PdCCKTETK
RC@jPFQ&XMU'0N4X!!'C[FTB$,l@qCTX%R9("-T%$99+q8T!!'8V"D,jBN3$aJm&
TZ5b4!e8CDA56DA16G@jNC@0TC'&LE'@6GfKPG'KPFT1qCTM"-T%$99+q5C%!mB1
j,T%%qSp8D'PcNfC[E'a[N!#XFRGcNfCbEff6G'KPNfCKBh56G'KKG*0dD'@1SBf
4'`!!GjUXFQpbC*B$(E4`FQpLE'9YNfC[FT0QFQ9PNh0PE@PRFQpeF(16DA16G@j
NC@0TC'&LE'8ZN36dMdPQNlj*N3320lPTFj0RC@jPFQ&dC@56BTKjNf'6FQ9MGA*
cDADBC@ajMU'0N4X!!'9ZQUabG@ePFQ&LE'@@"'deFf9d,*%%MGKdD'9ZNhHBCC0
RDADBCC0KNh0PE@NYC'9MDA0TEfk6F(*[N!"6MQ0PC(9bCC0dD'&dNfKKE(4cNfP
QNf&ZC*0[EQajNfPQMU'0N4X!!,jQN35G8F%bN3098Vj*N3$aJlNZN36YhdCTEQ&
XE(Q@!`QQGjUXFQ@6CAKKE@PZCC0KNf0XBA0cNfpQNfjTBf9XHC0LN!"6MQ9SBCK
fQ'9NNfPNC@&XFj0QEh+6GfKTBjKSNhHBC@&VNdGbIj(k)!4[BQjPFSkKMC%E!!"
LBA0PFjB$kUKMB@k6BT!!8ijPNf9KFfajNf0[EA"eG'9N,SkI'-@4MC%PX)BU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSUMTmIrmUKMC%E!!#l6@&bDjB%J!"6G'&ZDh9c,*1j3f&
XD@C[FQjTBCX$kUK3PDabEfajG'9MNfKZD@1B8h4KG'@B9@jTGT0PFR0TG*0jQ%p
QQ&0KETK-G@PcQ%pLDA0`N!"6MQq1SBf4'`!!Zd&`F'ajD@jRQ`2$98j[EQ0[E@f
9S!"eG'&dDAD6CCK(FRq4q8!!Ef*ZCA+B3Q&cDA1BG'qB8(*[BQaPEA1BD@kB3@j
KE(PcDA1BB@jNMU'0N4X!!%0[ET!!S!"dFQpXN35!!&4SC@pbHBkQSBf4'`!!Z94
SCA*PPJ-"8@&bCC0KNfk9V(*eEC0LN!"6MQ9bPJ-"8@pQNh4SC@pbC@ecNfPZNf&
ZB@ajFfPcNf&ZC*0MEfkDV(*dFQpXNh4SC@pbHC0hD'PMQ'L6D''BGTKPNf'6E@'
4!+FFDQpbMU'0N4X!!'&XCf9LFQ&TBjB%a*eMEfe`QP11EfjPET!!V(*d,T%(aVp
8D'PcNf&XCf9LFQ&TBj0MEfe`Q'pZC@k3!+abG*0MEfjcDA0dFj0[CT--EQ4TEQH
6BC0cHA0dC@f6EfD1SBf4'`!!E@&dFQPiPJ1MkQ9aG@&dD@pZFj0hD'PMQUabD*0
SBA16FfpYCC0NCA0TFQ&LE'@6F(*[F*!!8ijPFR5BHC-SC5jR,Lb4!l)3B@ePEQ&
LE'@6G'q6ETKeE@9bD@0KE)kKMC%E!!"cEfaeG'P[ELQ@!qUSB@jNNhGSD@1DV(*
SNfPcNf9aG@PfNIpBj'&XC@kBG*0dEj0KNfGTGTKPET0cHA0dC@f6EfD6E@&dFQP
iNf9aG@&dD@pZFbk1SBf4,*rd6h9bPJ0dm@9iF*!!8ijPFQPPEQ0PNfKKFj0cD'q
DV(*hET0dD'&dNh4bB@jcCQpbE@PZCj0dD'@6CfPfQ'9ZNh0jFh4PEC0[CT0YBA4
bDAL6CA&eB5f1SBf4'`!!G'P[ER1@!kFlD@kDV(*dEj0[EQ@6GfKTBjKSNfKKFj0
KNf4PFfPbB@*XCC0`FQp`N!"6MQ9bG*KjNf0KEQj[G*0LN!"6MQ@6C'pZCC0LQ(Q
6GA0TEQH6BC0ZEfjMEfdYMU'0N4X!!'f9V(*eG'&dDAD6CCB&%eT(FRq4qL!%Ef*
ZCA+63Q&cDA16B@aREh*TG'KYNf&XEfjP,T%)X[G2EQ@6BfpYE@pZNf0[EQ0PFQk
6DA16G'KKG*0KNfj[ELf1SBf4'`!!BfpYEC@XFR9dBA4TGT0PPJ3,AdGbIj[k)!4
[BQjPFT0#BA0TFj0MB@k6BT!!8ijPNfPZ$'jTG'@6B@jNNh0[Nh4SCC0ZEfjMEfe
YPDabGA4KG'PfNf@4"!YI4h*rQ'pLEQ9bMU'0N4X!!%*KFfPcPJ3f+f&XCfpbDA4
SEC0hD@aXNfjPGT!!V(*PFT0dCA*YD@jKG'8ZN3BEDPGSC@k6EfjPNh0dEh"cNh4
SCC0KE'G[FQPdD'dXN34*$''64h*rNISJ"'pLEQ9bMU'0N4X!!%*KFfPcPJ3AF'P
cNfj[G*0[BR4KD@jPC#k4"Emh9fKPG'KPFT0[FT0ZEh56G'KPNh0PG*0[CT0bC@a
KG'P[ER16Ef*dB@PZC@56DA16BC0(FRq4qL!%Ef*ZCA+1SBf4'`!!3Q&cDA-XN36
bCfeKETUXFRQ@",fREfD6G'KPNh*PE'&dD@pZFj0[BR4KD@jPC*0YBCKjNf+3!&1
1CC0MEfjMCA"dG@&XE(Q6FQ9NG@jNB@kBG*0QFQpYNh4SCBkKMC%E!!"`P911CA*
cF*0PBh4TGTUXFQ@@""EEEfD6G'KPNf&`F'aTBf&dD@pZNf+3!&11C@PZCj0MEfj
cD@4PFQ9N,T%&[AK'NIm&9QpbNh4SDA16FQ9KFfpZ,*%%)HGhQ'@6BfpZFfPNCA+
6G'KPMU'0N4X!!'C[E'a[N!#XFRGTEQH@!qUSB@4NDA4TEfjKE*0KE'G[FQPdD'd
kMUN5(4b0N5bIp#Ja+CB%Gip'D@jNNf'6E@PZD@eKE*0RC@jPFQ&dD@jRNh0PG*0
QEh+6B@k6D@4PB@b6+(0[Nh4SBA56EfjPNf0KET0bC@e[PDabGT0PN34hMf0[ELf
1SBf4'`!!Bf9`G(9KE'ajPJ2UU(*PC(9ZC'&ZQUabG*0TEQC[FQeKG'P[ET0RC@j
PFQ&dC@56BTKjNh4SCC0(FRq4qL!%Ef*ZCA+63Q&cDA16B@aREh*TG'KY+5k1TSf
4'`!!8fPZBf@@"-U*B@aXEjUXFRGTEQH6CQpbNf1BD'&ZCf9cNfpQNhD4reMNBA*
TB@*XCA16Bf&ZNf+3!&11CC0fQ'9bHC0eFf9QG@`XN38#JRHBCC0KE(0[Nf0[ER0
TC'9bNh4SCBkKMC%E!!"QEfaXEjUXFRGTEQH@!i9mB@4NDA4TEfjKE*0KE'G[FQP
dD'f6GfKTBjKSNfCKBfPXDA4KG'9cNh4SCC0TETKdFQq3!&11C(9MG'P[ET0[CT0
ZCAH6GT(r@14KFQPKBQaPFcU1TSf4,*rd+$)TPJA,(N0[EA"eG'@6C'9MEfe`QP1
1Eh0TG'P[ER16EfD6BC0YBA4bDAL6CAK`FQ9cFfP[ET0TET!!V(*dEj0KNf0[EA#
BEh0TG'P[ET0[CSkKMC%E!!"YBA4bDAL@!qUSCAK`FQ9cFfP[ER16GfKTBjUXFQL
6FQ9cF*!!8ijPBh56Bf9bG'&TET0aG@&XDA4KG'PfQ'@6D@jQEh*YBA4TEfiZMSk
I(J!!MC)!jj!!!MD1MSb,!!!!"`!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
!!!!!!!!!!!!!1S#J!U)46)fJr6k4l+!#Sfi8MD$pJC(XMC%XRr5j6h9bPJAaM@e
PG'K[QP11C'pXEfGjNfC[FT0NCA*TGQPZCj0dD'@6B@aRC@*bB@PMNf0[EA#BEfj
PET!!V(*dNfpQNf'6G'KPEh*PEC0eFf9cMU31J!#0N4X!!(4SCCX$[EjZEfjMEfe
YPDabGA4KG'PfNf@B4h*rNISJ"'pLEQ9bQ%*KFfPcQ'&XCfpbDA4SECKKEQ5BG'K
PQ(56Gj0[Q'&XCfpbDA4SEA1BE@9ZNh4TEfjPC)kKMC%E!!"KBTT6MQq9V(*fNf8
ZN3KC(e4SCCB%p@KYCA4SEjKNEfa[ChQ6BfpZFfPcG(16EfD6FR9ZEQPZCj0dD'9
cCC0dD(*PCC0KE'G[FQPdD'ecNfpZNf'6BfpY,BkKMC%E!!"`GA4PFTB&Pb4QEh+
6BC--EQPdCC0KE@peETUXFR56EfD6G'PYC5b4"J*$C'PcF'aKQ(PTEQH6G'KPNh*
PE'&dD@pZFj0[BR4KD@jPC#b4"J*$D''BGQPZCj0KMU'0N4X!!(#3!&11CA*cEfk
@!r49GQPPGj0dD'@6FQ9XBA4TEfjcNfpLG'&TEQ9N,*%$pX"YB@YTEQH6B@k3!+a
bHC0NCA0TFQ9NNf0[EQ0XGA0TEfjcNf*KFf9NNfpZNh4SCBkKMC%E!!"ZEfiYB@a
RC@*bB@PMPJ,S9f0[EA#3!&11EfjPETUXFR4cNfpQNh4SCC0dD'9[FQ9Y,*%$(!&
YB@YTEQH6B@kBHC0NCA0TFQ9NNf1BD'&ZCf9cNfpQNhD4reMNBA*TB@*XCA11SBf
4'`!!B@jNPJ2UU(*PF*T6MQ9KG'PZCj0dD'@6F(*[Q'0PFh16BA16EQ9MCA0cBA*
jNIm&9Lk1RaMKHif4*E#'+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+SkI)"ZdMC%E!!#l9QP
MG'pbN35!!&9QEQ&bEj!!S!"fFfYT,*B$kULj6(9ZC*09EQPfPDabCA*cDA56HBk
KMC%E!!#l3N95QU!!4de"6TB%J!"KEQ5638j*3dZ6,C0`FQpRFQ&YFj0QEh+6EQp
Z,@0[E@fBGA4KG'PfQ'@6B@aRC@*bBA11U4%X,k'0N4X!!,P8D'@@!lIQE'&cG*0
fQUabCA*cD@pZFj0[CT0dQ(HBEj0$Efe`GA4PFT0"E'GPBR*KNh"bEfGbB@ecNf&
bCC0NDA0MGA0cC@3ZN38Rp8pZCC0[CT0dD'9YMU'0N4X!!#KKGA4SEh+@!il2,C0
+,N*KBj@XFQZ6C@aTELb4!k%Z8h4[DfK[E'fE!il29@jTGT0PFR0TG*0j+CKTFjK
KQ(*KG'KPFTKP$Q0TC@k6G*K`FQpRFQ&YQ'C[FTKMB@aMG5f1SBf4'`!!E'&dD@j
RPJ3h+8GbIj(k)!4[BQjPFT0LBA0PFj0QEh+6Ch*KC'9NNf&XCf9LFQ&c,T%'(Q4
"EQpdD'9bNfpZCC-SBA9dD'pbFj-YNd%Z8*@XFQq3!&11C'p`E'9XEj0f,)kKMC%
E!!"@,P9QEQ&bEj!!V(*fFfYT,*X$02G*ER0dDA4eG'@@!`H,EfD66@&dD'9YBA4
TBh-XQ%e[E'4[N!#XFRD4reMNB6Z4!e-r6*(r"9C85#b66(9ZC#bB8hH3!+abC@4
PELQ6Bf&XBh9XBA4PFikKMC%E!!""EQPMN!#XFQXRFj%$kUKbCA0[E(9dD@pZ,Sk
QMC%XRr3U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSUMU'0N4X!!,Y+EfKZPJ5!!%SZNeH4rZ!
!BC!!S!"fFQPV,*1j9@jTGT@XFQ9bFfPdNhQ@!qUSEfD63f&XD@C[FQjTB5e6B@k
64'PPCfq1SBf4'`!!ZdGbIj(j3!"[BQjPFTB%J!"#BA0PFbb68Q9hFQPdCC05G@a
PFbb6B@jNNdeKG(*TH*0&H("bCA0cD@pZFikQSBf4'`!!Z94SDA1@!emNG'&XDj0
MEfjMCA*ZFj0dD'@6BA9dEfeKG'9NNh0TEA"XD3aMBA4TEfk6EfD6CAK`FQ9cFfP
[ER16GfKTBjUXFQL6D@kBGTK[E(DBCC0ZEfiYMU'0N4X!!'0[E@fDV(*eG'PZCjB
%hDjfNIpBj'&bD@&LE'9c,T%)%I&8D'@6G'9MQ'KZEfa[ChQ6D'&cNf+3!&11C@9
ZNf&`F'aTC@56G'q6G'KPNh0TEA"XD3aMBA4TEfk6EfD1SBf4'`!!E@&dFQPiPJ5
b5'&ZC*0[F*!!8ijPFQ&dEh+6G'KPEh*jNf9iF(*PFh0TEfjcNhGSD@13!+abD*0
KFQPcCC0TET0PEQGTEQ9PFQPZCj0KF("XD@0KG'P[ER-ZMU'0N4X!!&4SCCX&CN*
ZEfiYBfpYEC@XFR9dBA4TGT0PQ(D4reMNBA*TB@k6G*K[CTKdD'@B4h*rNISJ"'p
LEQ9bQ%*KFfPcQ%&XCfpbDA4SECKTFjKeFf9NQ(4[Q'GPELf1SBf4'`!!CA*KG'@
@"24bFQ9hFQPdCC0bG@aPFbk4#&Bq9j(r"9CPNhGTE'b6B@acEj0XEj!!8ij[Dj0
KG*0dD'@6F'KPEQpYC@j[ET0[CT0TEJaZDA4PNf*KFf9cNf&ZC)kKMC%E!!"TEA"
XD@0KG'P[ER1@!qUSCQpbNf&eG'pYBA4PC*0dD'9[FQ9YNh"bEj!!V(*fD@jR,Sk
I'1&lMC%PX)BU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSUMTmJ'l50N4X!!,Y6CA*RCAQ4")!
!@CEqi!"eHRCTER0VHC-XQ`2UU,P9EQPfPDabCA*cDA56HCK[CTK2FQ9REfk1SBf
4'`!!ZdY[FhTeE*B%J!"KE'GPBR*KFj0bC@aKG'9NNh4[NfLDS!"jF*!!B!"PFR"
XB@jPNf&bFQ&ZCf9YC@kBG(16B@jNNfGbBA"SFikQSBf4'`!!Z8PZPJ0SDR4SCC0
dB@aV,*%$JRChQUabCC0NDA0MGA0cNh4SCC02FQaTDbe6Efa[E@pZNf&XCf9LFQ&
c,T%&$AC6G@1BD*0KET0KE'GPBR*KNlj"NlPTFj0KNf0[ECKLD5f1SBf4'`!!EQ&
dEh*TB@b@!dGGD@kDV(*dCA*`FQ9dBA4TEfk6EfD6G'KPNf0[D'pYEfa[ChQ6B@a
RC@*bBC0[CT0dD'@6BfpYF'aPE@9ZQ(56EfD6BC0MEfe`E'9iMU'0N4X!!'L9V(*
jF*!!8ijPFR"XB@jPQ`2l0Q&bFQ&ZCf9YC@k6G#k4"@U,[N'BZ@KKFjKKQ(0dB@j
NBA*N,*%$reTcEjKMB@aXC@5BA'*bEfZ6C@kBBfPbBh9TG#+BBQ&cDA-ZN39ULdD
4r`9@Eh+1SBf4'`!!G'KPPJ96HhHDV(*PE'`YFh4eC'PPC*0ME'&cFj0[CT0cGA#
3!&11CA*cEfafNIpBj'&LE'@6BA*bB@jRC@ePETKdFj0dD'PcNf*KFfPcNfKKFj0
KNhDBCA*jNfjTBf@1SBf4'`!!F(*[F*!!8ijPFR5DV(*jPJ@jSh4SBA56B@aXEjK
hFj0eFj0dEj0NC@C[FQf6[N'6ZA4[Nf'6E@pZEfeTB@b6B@aRC@*bBC1q3BfI!Fc
-[$#1N3TjTlPNC3aZC@56BTKjNf'1SBf4'`!!Ch*KF'JZN38*Re0dG@4jD@jRPJ0
Fj''6BQ&cDA16EfD6[N'0R`(-c,``MT%)(1LjGjUXFQ@6FQ9MEjKfQ'9bNh4SBA5
6DA56DA165fpcHR9XNbKKNh4SC@pbC@f6BTKjNdD4r`9@FRq4qL!%Ef+3!&11CA*
R+BkKMC%E!!"KEQ5@!p3aEf*dB@PZNf&ZNf9XC@GKETUXFR56CQpbECKeE''6CQp
bNfPdFj0)D@aLN!"6MQ9bG*0cCA*TCA-ZN38aBe4SC@k64(*TEQCPE'3RFj0NC@C
[FQeKG'P[ESkKMC%E!!"dD'9[FRQ@!qUSD@e`E'PPFj0dD'&dNlj"NlPTFj0,Eh0
kG@`ZMTmBiAZ0N5@`KLSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LS
U+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LSU+LU1MTmH!!#0NJ$RN!!#0ik
1M2J!!%N$!B15`"`l!!!!!!2S!U)46!'k!!!!"3!(mal#eNkJ!!jQCJ!-!!!!"Q0
YBRJa-[-FQlZ)3!!-!!!!$!!!!!CMEA4T-6,c'('K*3X!"J!!!!B!!!!&BfecH6E
c&lj,b!X!#!!!!!J!!!!&BfecH6Mc&L%L,*S!$!!!!!S!!!!'BfecH6%`ma6A!4F
b!!J!!!!)!!!!"@0YE@Nima1hi@HM!!`!!!!-!!!!"Q0YE@Na-[-4I(YC"`!)!!!
!#!!!!!4MEA)ima$#eNkJ!!`!!!!-!!!!"Q0YBRJa-[-2402YG!!44ki!%8HZ!!9
MEA)a0r-1@+Y4#`!-!!!!$!!!!!9MEA)a-[N!!&@I!YrIhprIhpm'a3!!:

--=====================_853959217==_
Content-Type: text/plain; charset="us-ascii"

_____________________
NMSU Math Dept
Rose Marquez (rosmarqu@nmsu.edu)
tel: (505) 646-3904, fax: (505) 646-1064

--=====================_853959217==_--


